%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
\documentclass[letterpaper]{twentysecondcv_en} % a4paper for A4

% If you don't need one of the below elements, remove the content inside the brackets {} leaving the command, e.g. \cvnumberphone{}

\profilepic{} % Profile picture

\cvname{Guilherme \newline Patriota} % Name
\cvjobtitle{Data Scientist} % Job title/career

\cvdate{} % Date of birth

% Short address/location, use \newline if more than 1 line is required
\cvaddress{H4V 2Y2 \newline Montreal/QC}
\cvnumberphone{+1 (438) 926-0872} % Phone number
\cvsite{linkedin.com/in/guilhermepatriota} % Personal website
\givenfacebook{}
\givenlinkedin{}
\cvmail{gdp.ai.data.eng@gmail.com} % Email address

%-------------------------------------------------------------------------------

\begin{document}

%-------------------------------------------------------------------------------
% ABOUT ME
%-------------------------------------------------------------------------------
\aboutme{Passionate about technology and data science, I am an experienced data 
scientist and developer with a strong background in electronics and 
telecommunications, as well as a master's degree in electrical engineering. 
Since 2016, I have been a software engineering and data science professor at 
UNINTER in Brazil, where I created a practical activity system with real-world 
cases from the job market for all IT courses. I am currently looking for new 
professional opportunities in my areas of interest.}
% To remove the About Me section, delete everything within \aboutme{}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{
				{Electronics, IoT, MQTT/4.5},
				{Machine Learning, NLP/5},
				{Database, SQL, NoSQL/4.5},
				{Big Data, Hadoop, Spark/4},
				{Statistical Analysis/5},
				{Pandas, Tensorflow, AI/5},
				{Programming, Python, C++, R/6}}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6
\skillstext{{French/5}, {English/5}, {Portuguese/6}}

%----------------------------------------------------------------------------------------
% Portfolio text section
\portfolio{github.com/guipatriota}

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{since 2016}
						{University Professor}
						{UNINTER and FAESP, Brazil}
						{\emph{- Courses: System Analysis, Big Data, Natural Language 
						Processing, Databases, NoSQL, Embedded Systems, Artificial 
						Intelligence, Electronics, C and Python Programming.\\
						\textbf{$\star$ Achievement:} Created a system of practical 
						activities with real cases from the job market for all IT courses
						(Big Data, NoSQL and Python).}}
	\twentyitem{2020-2021}
						{C++ Developer}
						{Boa Impressão 3D, Brazil}
						{\emph{- Developing electronics and software for new equipment.\\
						- Managing the assembly line.\\
						\textbf{$ \star $ Achievement:} Creation of a high-capacity 3D 
						printer (C++).\\
						\textbf{$ \star $ Achievement:} Implementation of a production line 
						control and maintenance system based on Key Performance Indicators 
						(KPIs) with Python.}}
	\twentyitem{2018-2020}
						{3D Printer Technician}
						{GS3D, Brazil}
						{\emph{- Building, repairing, and configuring 3D printers.\\
						- Conducting 3D modeling and research on healthcare projects.\\
						\textbf{$ \star $ Achievement:} Creation of a company focused on 
						meeting hospital needs.}}
	\twentyitem{2012-2018}
						{Medical Equipment Engineer}
						{Hospitals in Brazil}
						{\emph{- Maintaining and repairing medical equipment.\\
						- Managing teams of technicians.\\
						\textbf{$ \star $ Achievement:} Creation of a project management 
						department based on PMBOK.\\
						\textbf{$ \star $ Achievement:} Implementation of a clinical 
						engineering and medical equipment traceability department with 
						management software on React platform (Javascript).}}
\end{twenty}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2022}
						{Specialization in Online Learning}
						{UNINTER, Brazil}
						{\emph{Online pedagogy, flipped classroom, and other learning 
						techniques.}}
	\twentyitem{2016}
						{MBA in Healthcare}
						{FGV, Brazil}
						{\emph{Improvements in healthcare service management.}}
	\twentyitem{2011}
						{M.Sc. in Electronic Engineering}
						{UFPR, Brazil}
						{\emph{Applied AI to electronics and telecommunications.}}
	\twentyitem{2006}
						{B.Sc. in Electronic Engineering}
						{UFPR/ENSPS, Brazil/France}
						{\emph{Sandwich degree in electronic engineering and 
						telecommunications.}}
\end{twenty}

%----------------------------------------------------------------------------------------
% COURSES
%----------------------------------------------------------------------------------------

\section{Additional Training}

\begin{twenty} % Environment for a list with descriptions
\twentyitemmedium{2020}{Knowledge Discovery in Databases and Data Mining}{\emph{UFPR, Brazil}}
\twentyitemmedium{2020}{Foundations of Data Science}{\emph{Aldeia Coworking, Brazil}}
\twentyitemmedium{2020}{Introduction to Python Programming}{\emph{MITx, USA}}
\twentyitemmedium{2020}{Fundamentals of AI}{\emph{Data Science Academy, Brazil}}
\twentyitemmedium{2020}{Datascience 2.0}{\emph{Data Science Academy, Brazil}}
%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
% VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Volunteer Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2020}
						{3D Printer Technician}
						{GS3D, Brazil}
						{\emph{Development, 3D printing, and delivery of 500 visors for 
						donation to healthcare professionals during the first 6 months of 
						the COVID-19 pandemic.}}

\end{twenty}

%----------------------------------------------------------------------------------------
% INTERESTS
%----------------------------------------------------------------------------------------

\subsection{Hobbies and Interests}

- Professional: Teaching, AI, Blockchain, 3D Printing, Research.\
- Personal: Dance, Scouting

*References available upon request

\end{document}